---
title: "Lab 5 Assignment"
author: "Michael Slaughter"
date: "2021-02-24"
output: github_document
---

Welcome To My Lab 5 Assignment

Here is where we load in the data

```{r message=FALSE}
library(tidyverse)
iris <- as_tibble(iris)

```

## Question 1

Rename each variable so that it is all lower-case and uses an underscore _ instead of a period . in the name (the recommended coding style in the tidyverse style guide). Print the resulting table.

```{r}
rename(iris, 
sepal_length = Sepal.Length,
sepal_width= Sepal.Width,
petal_width=Petal.Width,
petal_length = Petal.Length)
iris2 <- rename(iris, 
             sepal_length = Sepal.Length,
             sepal_width= Sepal.Width,
             petal_width=Petal.Width,
             petal_length = Petal.Length)
iris2
```

## Question 2

Convert the four numerical variables from cm to mm by multiplying by 10. Print the resulting table.

```{r}
mutate(iris2,
       sepal_length=sepal_length*10,
       sepal_width=sepal_width*10,
       petal_width=petal_width*10,
       petal_length=petal_length*10)
```

## Question 3

Calculate sepal area and petal area (area is equal to length multiplied by width). Print a table with only the variables sepal area, petal area, and species.

```{r}
thing_with_areas <-
mutate(iris2,
       sepal_area = sepal_length * sepal_width, 
       petal_area = petal_length * petal_width)

select(thing_with_areas, Species, sepal_area, petal_area)

```

## Question 4

Calculate the following statistics for the entire dataset from the sepal length variable and print the resulting table:

sample size
maximum value
minimum value
range
median
first quartile (q1)
third quartile (q2)
inter-quartile range (iqr)

```{r}
summarize(
        iris2,
        sampl_size= n(),
        max_sepal_length = max(sepal_length),
        min_sepal_length = min(sepal_length),
        range_sepal_length = max(sepal_length)-min(sepal_length),
        med_sepal_length = median(sepal_length),
        q1 = quantile(sepal_length, probs=0.25),
        q3=quantile(sepal_length, probs=0.75),
        IQR_sepal_length = IQR(sepal_length)
        )
```

## Question 5

Calculate the following statistics for each species from the petal width variable and print the resulting table:

sample size
mean
standard deviation
variance
standard error of the mean
approximate 95% confidence interval

```{r}
petal_grouped<- group_by(iris2,Species)
# petal_grouped
petal_widthsummary <-
        summarize(
                petal_grouped,
                sampl_size = n(),
                mean_petal_width = mean(petal_width),
                sd_petal_width = sd(petal_width),
                var_petal_width = var(petal_width),
                sem_petal_width = sd_petal_width / sqrt(sampl_size),
                ci_upper_limit = mean_petal_width + 1.96 *
                        sem_petal_width,
                ci_lower_limit = mean_petal_width - 1.96 * sem_petal_width
        )
petal_widthsummary
```

## Question 6

Visualize the relationship between petal width and species using a strip plot.

```{r}
ggplot(data = iris2) +
        geom_jitter(mapping = aes(x = Species, y = petal_width))

```

## Question 7

Starting with the previous graph, add the mean and 95% confidence interval for each species

```{r}
ggplot(data = iris2)+
        geom_jitter(mapping=aes(x=Species,y=petal_width))+
        geom_crossbar(
                data=petal_widthsummary,
                mapping=aes(x=Species,y=mean_petal_width, ymax = ci_upper_limit,
                            ymin = ci_lower_limit))
```

## Question 8

Visualize the relationship between petal length, petal width, and species using a scatterplot. Map the two numerical variables to the x and y axes and map species to the color and shape aesthetics.

```{r}
ggplot(data = iris2)+
        geom_point(mapping=aes(x=petal_length,y=petal_width,color=Species,shape=Species))
        
```

sessioninfo()

